---
title: "Project Phase Plots"
author: "Brian"
date: "1/23/2022"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
df <- read_csv("Projects - January 22, 2022.csv")
```

```{r}
#tidyverse glimpse
glimpse(df, width = 100)
```

getting the data together

```{r}
df2 <- df %>% select(Phase, Master)

tab_All <- df2 %>% select(-Master) %>% table() %>% as_tibble() %>% rename(Phase = ".", Count = n)
tab_M_Yes <- df2 %>% filter(Master == "Yes") %>% table() %>% as_tibble() %>% rename(Count = n)
tab_M_No <- df2 %>% filter(Master == "No") %>% table() %>% as_tibble() %>% rename(Count = n)

title_Text <- 'Total number of projects by phase'
X_axis_title <- 'Project Phases'
max <- as.integer(max(tab_All$Count)) 
```

Getting the first graph together

```{r All}
data <- tab_All
data$Phase <- factor(data$Phase, levels = c('PLANNING',
                                            'PREDESIGN',
                                            'DESIGN',
                                            'IMPLEMENT',
                                            'CLOSEOUT',
                                            'HOLD',
                                            'NOT SET'))
base <- ggplot(data, aes(x = Phase,
                         y = Count,
                         label = Count)) +
  theme_classic()

lolliplot_All = base + 
  geom_segment(aes(y = 0, 
                   yend = Count, 
                   x = Phase, 
                   xend = Phase),
               color = "gray")  +
  
 geom_point(size = 4, color = "Blue") +
  geom_text(nudge_x=0.3,show.legend = FALSE) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(0, max)) + 
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.line.x = element_blank()) +
  labs(title = title_Text) +
  xlab(X_axis_title)
```

Replicating the data with each graphs

```{r Master}
data <- tab_M_Yes
data$Phase <- factor(data$Phase, levels = c('PLANNING',
                                          'PREDESIGN',
                                          'DESIGN',
                                          'IMPLEMENT',
                                          'CLOSEOUT',
                                          'HOLD',
                                          'NOT SET'))
base <- ggplot(data, aes(x = Phase,
                   y = Count,
                   label = Count)) +
  theme_classic()

lolliplot_M_Yes = base + 
  geom_segment(aes(y = 0, 
                   yend = Count, 
                   x = Phase, 
                   xend = Phase),
               color = "gray")  +
  
 geom_point(size = 4, color = "Blue") +
  geom_text(nudge_x=0.3,show.legend = FALSE) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(0, max)) + 
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.line.x = element_blank()) +
  labs(title = "Count of Master Projects by Phase") +
  xlab(X_axis_title)
```

Second Graph

```{r master}
data <- tab_M_No
data$Phase <- factor(data$Phase, levels = c('PLANNING',
                                          'PREDESIGN',
                                          'DESIGN',
                                          'IMPLEMENT',
                                          'CLOSEOUT',
                                          'HOLD',
                                          'NOT SET'))
base <- ggplot(data, aes(x = Phase,
                   y = Count,
                   label = Count)) +
  theme_classic()

lolliplot_M_No = base + 
  geom_segment(aes(y = 0, 
                   yend = Count, 
                   x = Phase, 
                   xend = Phase),
               color = "gray")  +
  
 geom_point(size = 4, color = "Blue") +
  geom_text(nudge_x=0.3,show.legend = FALSE) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(0, max)) + 
  theme(axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.line.x = element_blank()) +
  labs(title = "Count of Sub Projects by Phase") +
  xlab(X_axis_title)
```

```{r}
## All Airport Projects
lolliplot_All
## All Master Projects
lolliplot_M_Yes
## All Non-Master Projects
lolliplot_M_No
```

My attempt at a faccet wrap. I can go back and dropt the titles, then do colors = Phase and have the legend in the bottom right

```{r}
library(ggpubr)
ggarrange(lolliplot_M_Yes, lolliplot_M_No, lolliplot_All,
          ncol = 2, nrow = 2)
```

# Note to Professor Jose Manuel

We will pick from one of the above plots based on the best use for our client. All projects, master projects or sub projects. We may do some combination of the three
